Dependent Object Types

### 2012-08-10 article.tex
getting rid of known counterexamples

\subsubsection{Set of Values}
$\relv k \Gamma s T$ defines the set of values that appear to have
type $T$ when taking at most $k$ steps. $\Gamma$ and $s$ must agree:
$\dom(\Gamma) = \dom(s)$ (ordered) and $\forall (x : T) \in \Gamma, x
\in \relv k \Gamma s T$. A variable $y$ belongs to $\relv 0 \Gamma s
T$ simply by being in the store. In addition, it belongs to $\relv k
\Gamma s T$ for $k > 0$, if it defines all type, method and value labels in
the expansion of $T$ appropriately for $j < k$ steps.
\begin{align*}
&\relv k \Gamma s T = \{ y \ |\\
&\gap \Gamma \ts T \wfe \andl\\
&\gap y \in \dom(s) \andl\\
&\gap \forall j < k,\\
&\gap y \mapsto T_c \ldefs{\seq{l = v}\;\seq{m(x)=t}} \in s,\\
&\gap \Gamma \ts T \expand_y \seq{D},\\
&\gap (\forall L_i : S \rightarrow U \in \seq{D},\\
&\gap\gap \Gamma \ts y \ni L_i \typ {S'..U'}) \andl\\
&\gap (\forall m_i : S \rightarrow U \in \seq{D},\\
&\gap\gap t_i \in \rele j {\Gamma \envplus{x_i : S}} s U) \andl\\
&\gap (\forall l_i : V \in \seq{D},\\
&\gap\gap v_i \in \relv j \Gamma s V)\\
&\}
\end{align*}

This relation captures the observation that the only ways for a term
to get stuck is to have a field selection on an uninitialized field or
a method invocation on an uninitialized method. However, a {\it potential
  pitfall} is that the value itself might occur in the types $S$, $U$,
$V$, because we substitute it for the ``self'' occurrences in the
expansion, so the relation makes sure that the type labels exist.

>>>>

\subsubsection{Set of Values}
$\relv k \Gamma s T$ defines the set of values that appear to have
type $T$ when taking at most $k$ steps. $\Gamma$ and $s$ must agree:
$\dom(\Gamma) = \dom(s)$ (ordered) and $\forall (x : T) \in \Gamma, x
\in \relv k \Gamma s T$. A variable $y$ belongs to $\relv 0 \Gamma s
T$ simply by being in the store. In addition, it belongs to $\relv k
\Gamma s T$ for $k > 0$, if it defines all type, method and value labels in
the expansion of $T$ appropriately for $j < k$ steps.
\begin{align*}
&\relv k \Gamma s T = \{ y \ |\\
&\gap y \in \dom(s) \andl (\\
&(\Gamma \ts T \wfe \andl\\
&\gap \forall j < k,\\
&\gap y \mapsto T_c \ldefs{\seq{l = v}\;\seq{m(x)=t}} \in s,\\
&\gap \Gamma \ts T \expand_y \seq{D},\\
&\gap (\forall m_i : S \rightarrow U \in \seq{D},\\
&\gap\gap t_i \in \rele j {\Gamma \envplus{x_i : S}} s U) \andl\\
&\gap (\forall l_i : V \in \seq{D},\\
&\gap\gap v_i \in \relv j \Gamma s V)) \orl\\
& (T = T_1 \tand T_2 \andl y \in \relv k \Gamma s {T_1} \andl y \in \relv k \Gamma s {T_2}) \orl\\
& (T = T_1 \tor T_2 \andl  (y \in \relv k \Gamma s {T_1} \orl y \in \relv k \Gamma s {T_2}))\\
&\}
\end{align*}

This relation captures the observation that the only ways for a term
to get stuck is to have a field selection on an uninitialized field or
a method invocation on an uninitialized method. However, a {\it potential
  pitfall} is that the value itself might occur in the types $S$, $U$,
$V$.
